Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-10 examples.tex
+

$\specline{ \forall_{i\in \textssf{0 ... 511} } \ldotp  \textsf{entry\_val }_{\textsf{pfn}} + \texstf{i * 8} \mapsto_{\textsf{id}} \textsf{\_} \ast  \textsf{qfrac} = 1 \land \lnot(\textsf{entry\_present entry\_val }_{\textsf{pfn}} + \texstf{i * 8})  }$

>>>>

$\specline{ \forall_{i\in \textsf{0 ... 511} } \ldotp  \textsf{entry\_val }_{\textsf{pfn}} + \textsf{i * 8} \mapsto_{\textsf{id}} \textsf{\_} \ast  \textsf{qfrac} = 1 \land \lnot(\textsf{entry\_present entry\_val }_{\textsf{pfn}} + \textsf{i * 8})  }$
